Marlowe: implementing and analysing financial contracts on blockchain

### 2019-12-09 papers/marlowe2019/paper.tex
Finalising bibliography, Beginning coonclusions.

\paragraph{TO DO}

Add stuff on BitML, DAML, \ldots.

\section{Future work and conclusions}

>>>>

BitML~\cite{BitML} is a DSL for specifying Marlowe-like contracts that regulate transfers on the Bitcoin blockchain. BitML is implemented via a compiler that translates contracts into standard Bitcoin transactions. Participants execute a contract by appending these transactions on the Bitcoin blockchain, according to their strategies, which also involve the exchange of bitstrings that guarantee to a very high probability the correctness of contract execution. Marlowe is directly implemented by an interpreter which could also be implemented on a covenant-based~\cite{covenants} extension of the Bitcoin blockchain.

\section{Conclusions and future work}

Conclusions (draft)
\begin{itemize}
\item
Using a DSL means that we can d o much better with analysis and proof than a general purpose language.
\item
Defining the language by means of an executable reference semantics means that we can, as well as directly executing this semantics, generate an on-chain interpreter for it and simulate it in browser using the Haskell-like languages Plutus and PrueScript. This is made particularly straightforward by working in the subset of Haskell that directly corresponds to what translates directly into these languages.
\item

\end{itemize}
